Non-Vertical Cultural Transmission and the\\ Evolution of Cooperation

### 2020-09-01 ms/main.tex
Move WOODCOCK 2006 paper to intro

@@

\autoref{fig:results2}b illustrates these conditions, where
 the third equilibrium given by Eq.\ \ref{eq:vert_hori_equilibrium} becomes
\begin{equation} \label{eq:vert_hori_alpha0_equilibrium}
\tilde{p}^*(\alpha=0) = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B) },
\end{equation} 
and the cost boundaries are
\begin{equation}\begin{aligned}
\gamma_1(\alpha=0) = \frac{T_A - T_B}{1-T_B}, \quad
\gamma_2(\alpha=0) = (1+b)\frac{T_A - T_B}{1-T_B}.
\end{aligned}\end{equation}
If $T_A>T_B$ then $0<\gamma_1(\alpha=0)<\gamma_2(\alpha=0)$.
So either $c<\gamma_1(\alpha=0)$ or $\gamma_1(\alpha=0)<c<\gamma_2(\alpha=0)$ will allow fixation of cooperation, the latter only if the initial frequency is high enough.
If $T_A<T_B$ then $\gamma_2(\alpha=0)<\gamma_1(\alpha=0)<0<c$,
and defection will fix.
%TODO add "effective cost" argument: c<TA-TB/(1-TB) <=> 1-(1-c)(1-TB)<TA.
\\

>>>>

\citet{woodcock2006significance} showed the importance of non-vertical transmission for the evolution of cooperation. In their model the individuals interact according to standard prisoner dilemma game in which two individuals who interact can cooperate or not.
In their work they do not link between interaction and transmission. Their model illustrates that it
is possible to sustain altruistic behaviour at the level of culture for a significant
period of time in the absence of any direct biological propensity favouring this
behaviour.

@@

\autoref{fig:results2}a illustrates these conditions, where
 the third equilibrium given by Eq.\ \ref{eq:vert_hori_equilibrium} becomes
\begin{equation} \label{eq:vert_hori_alpha0_equilibrium}
\tilde{p}^*(\alpha=0) = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B) },
\end{equation} 
and the cost boundaries are
\begin{equation}\begin{aligned}
\gamma_1(\alpha=0) = \frac{T_A - T_B}{1-T_B}, \quad
\gamma_2(\alpha=0) = (1+b)\frac{T_A - T_B}{1-T_B}.
\end{aligned}\end{equation}
If $T_A>T_B$ then $0<\gamma_1(\alpha=0)<\gamma_2(\alpha=0)$.
So either $c<\gamma_1(\alpha=0)$ or $\gamma_1(\alpha=0)<c<\gamma_2(\alpha=0)$ will allow fixation of cooperation, the latter only if the initial frequency is high enough.
If $T_A<T_B$ then $\gamma_2(\alpha=0)<\gamma_1(\alpha=0)<0<c$,
and defection will fix.
%TODO add "effective cost" argument: c<TA-TB/(1-TB) <=> 1-(1-c)(1-TB)<TA.
\\
